deckard: A Declarative Tool for Machine Learning Robustness Evaluations

### 2025-12-09 paper.tex
Commit from GitHub Actions (Render R Markdown)

The software package presented, called \texttt{deckard}, is a modular
toolkit that streamlines and standardizes machine learning (ML)
experimentation, with a particular emphasis on evaluating models under
worst-case perturbations(Goodfellow, Shlens, and Szegedy 2014). It
offers a flexible, extensible framework for defining, running, and
analysing end-to-end ML pipelines in settings where inputs may be
manipulated by an attacker or corrupted by unexpected noise (Biggio et
al. 2013).

@@

>>>>

The software package presented, called \texttt{deckard}, is a modular
toolkit that streamlines and standardizes machine learning (ML)
experimentation, with a particular emphasis on evaluating models under
worst-case scenarios (Goodfellow, Shlens, and Szegedy 2014). It offers a
flexible, extensible framework for defining, running, and analysing
end-to-end ML pipelines in settings where inputs may be manipulated by
an attacker or otherwise experience unexpected noise (Biggio et al.
2013).

@@

To avoid any ambiguity about contributions, we clarify that
\texttt{deckard} is a software system introduced in this work. Although
the implementation is publicly available on GitHub, the modular design,
configuration-driven framework, and presentation of the source code are
unique to this paper. While the prior works outlined in the next section
can be fully reproduced with this software, this paper is the first to
present the system as a cohesive method, fully specified, documented,
and intended for broad reuse.
